---
title: "Introduction"
author: "Ana Comesana"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(devtools)
library(binomial)
```

# Binomial Package - Ana Comesana
I created this package for the purpose of completing the **workout 3** assignment for Stat 133 at UC Berkeley. The following binomial package contains functions, objects and methods regarding binomial distributions.

## Basic Statistics Functions
The most basic functions in this package are those to calculate different statistics on the binomial distribution of the user's choice. The user will be able to calculate the mean, variance, skewness, and more of the binomial distribution. 

```{r}
number_trials <- 5
probability_success <- 0.5
```

#### Mean
```{r}
bin_mean(number_trials,probability_success)
```

#### Variance
```{r}
bin_variance(number_trials,probability_success)
```

#### Mode
```{r}
bin_mode(number_trials,probability_success)
```

#### Skewness
```{r}
bin_skewness(number_trials,probability_success)
```

#### Kurtosis
```{r}
bin_kurtosis(number_trials, probability_success)
```

All of these measures have the following constraints:
- probability must be a number between 0 and 1
- number of trials must be non-negative

## Other Distribution Objects
This package also has the option of creating the following distribution objects:
- bindis
- bincum
Both of them inherit from the object data.frame.

#### Binomial Distribution Objects
The 'bindis' objects are displayed as a data.frame with columns for number of successes and probability that we will achieve that numbe of successes.

```{r}
#Arguments
trials <- 5 
prob <- 0.5

#Binomial Distribution Object
binom_dist <- bin_distribution(trials, prob)

# 'bindis' as data.frame
binom_dist

# plot() will plot our 'bindis' object
plot(binom_dist)
```

#### Cumulative Binomial Distribution Objects
The 'bincum' objects are also displayed as a data.frame, much like 'bindis', except they also include a column showing the cumulative probability of each success.

```{r}
# Arguments
trials <- 5
prob <- 0.5

# Cumulative Binomial Distribution object
cum_dist <- bin_cumulative(trials,prob)

# 'bincum' as data.frame
cum_dist

# plot() will plot our 'bincum' object, different from 'bindis'
plot(cum_dist)
```

##Binomial Variable Object

The final element in this package is a Binomial Variable object, which has class 'binvar'. This object represents a random variable for our binomial distribution, and the user may initialize it by simply calling 'bin_variable()'

```{r}
#Arguments
trials <- 5
prob <- 0.5

#Binomial Variable Object
bin_var <- bin_variable(trials,prob)

# Displaying object
bin_var

# summary() of 'binvar'
bin_var_sum <- summary(bin_var)
bin_var_sum
```

